### 2024-10-07 esop25/cpj.tex
checkpoint

\begin{lemma}
  \label{lemma-cpjsound}
  If $\cpj{R}{\eqs}{\eqspre \wedge \toeq{\prog}}{\Gamma}$ is valid then $\Gamma$ is
  sound for $\prog$.
\end{lemma}
\begin{proof}
  Unrolling Definition \ref{definition-sound}, proceed by induction on $M'$.
  In case $M' = \varnothing$ the result follows trivially. Otherwise
  $M' = M_0 \cup \{ \mx{w}{\cid} \}$ and wlog $\Gamma = \Gamma_0; \mx{w}{\cid} : \ty_0$
  and $\prog = \prog_0;\xassign{\mx{w}{\cid}{\be}{\cid_0}$, where
    $\cpj{R_0}{\eqs}{\eqspre \wedge \toeq{\prog_0}}{\Gamma_0}$ is valid.    
\end{proof}

>>>>

\begin{lemma}
  \label{lemma-cpjsound}
  If $\cpj{R}{\eqs}{\eqspre \wedge \toeq{\prog}}{\Gamma}$ is valid then $\Gamma$ is
  sound for $\prog$.
\end{lemma}
\begin{proof}
  Unrolling Definition \ref{definition-sound}, proceed by induction on $M'$.
  In case $M' = \varnothing$ the result follows trivially. Otherwise
  $M' = M_0 \cup \{ \mx{w}{\cid} \}$ and wlog $\Gamma = \Gamma_0; \mx{w}{\cid} : \ty_0$
  and $\prog = \prog_0;\xassign{\mx{w}{\cid}}{\be}{\cid_0}$, where
  $\cpj{R_0}{\eqs}{\eqspre \wedge \toeq{\prog_0}}{\Gamma_0}$ is valid.    
\end{proof}
